\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-13 paper/mswp2012-proposal.tex
paar änderungen an indroduction

>>>>

In the Forbes List for the fattest nation, Austria is on place 52 with a fat rate of 57.1\%.\footnote{\url{forbes list: http://www.forbes.com/2007/02/07/worlds-fattest-countries-forbeslife-cx_ls_0208worldfat_3.html}}. The Image on this site show the percentage of obese people in the European Union for male and femals.

\begin{figure}[tb]
	\centering
	\includegraphics[width=1\textwidth]{images/introduction/1.jpg}
	\caption{Obese in the EU}
	\label{fig:obese_in_eu_pdf}
\end{figure}

Unfortunately this trend starts early. The parents live unhealthy and show their children this unhealthy way of live. The children are overweight in young ages. And this can raise the impact on the life of the child when it is grown up. \\

You can't teach an old dog new tricks. So the children are grown up without any real chance to live in a healthier way. But this slogan is not true at all. It is never too late for change something. But it gets more difficult. \\
